Application of Network Flow and Linear Programming to Scheduling of Clinicians

### 2019-08-19 paper/paper.results.tex
Replace divisions graph with table
Move divisions results to end of results section, rewrite its analysis portion

We begin by evaluating the runtime in a single-division department, with an increasing number of clinicians, over a 1-year time-span. Figure \ref{fig:avg-runtime-clinicians} shows the average runtime in seconds of 10 runs, for different numbers of clinicians, $C = \{5, 10, 15, 25, 50, 100\}$. From the graph, we can see that the LP formulation performs extremely well on a typical hospital department with no more than 30 clinicians [ref \ref{??}], and can even handle busier departments with upwards of 100 clinicians. \\

\begin{figure}[h]
	\centering
	\includegraphics[scale=.7]{fig/avg_runtime_clinicians}
	\caption{Plot of average runtime for LP with an increasing number of clinicians}
	\label{fig:avg-runtime-clinicians}
\end{figure}

Next we evaluate the effect of increasing the number of departments. Figure \ref{fig:avg-runtime-divisions} shows the average runtime for a department with 10 clinicians, and a range of divisions, $D = \{1, 2, 3\}$. We can see that increasing the number of divisions even by 2 greatly affects the runtime. The LP solver had significant trouble when we increased the number of divisions further, making it impractical to quickly generate schedules for departments with many divisions. \\

\begin{figure}[h]
	\centering
	\includegraphics[scale=.7]{fig/avg_runtime_divisions}
	\caption{Plot of average runtime for LP with an increasing number of divisions}
	\label{fig:avg-runtime-divisions}
\end{figure}

@@

We evaluate the effect of a longer time-horizon on the runtime of the algorithm. Figure \ref{fig:avg-runtime-blocks} presents the average runtime over 10 runs for an increasing number of 2-week blocks $B = \{26, 52, 78, 104\}$ to simulate a department that generates schedules for a few years in advance. We can see that there is an increasing trend in the runtime, however the solver is still able to find an optimal schedule for a 4-year time horizon in a very reasonable amount of time.

@@

>>>>

%We begin by evaluating the runtime in a single-division department, with an increasing number of clinicians, over a 1-year time-span. Figure \ref{fig:avg-runtime-clinicians} shows the average runtime in seconds of 10 runs, for different numbers of clinicians, $C = \{5, 10, 15, 25, 50, 100\}$. From the graph, we can see that the LP formulation performs extremely well on a typical hospital department with no more than 30 clinicians [ref \ref{??}], and can even handle busier departments with upwards of 100 clinicians. \\

%\begin{figure}[h]
%	\centering
%	\includegraphics[scale=.7]{fig/avg_runtime_clinicians}
%	\caption{Plot of average runtime for LP with an increasing number of clinicians}
%	\label{fig:avg-runtime-clinicians}
%\end{figure}

%Next we evaluate the effect of increasing the number of departments. Figure \ref{fig:avg-runtime-divisions} shows the average runtime for a department with 10 clinicians, and a range of divisions, $D = \{1, 2, 3\}$. We can see that increasing the number of divisions even by 2 greatly affects the runtime. The LP solver had significant trouble when we increased the number of divisions further, making it impractical to quickly generate schedules for departments with many divisions. \\

%\begin{figure}[h]
%	\centering
%	\includegraphics[scale=.7]{fig/avg_runtime_divisions}
%	\caption{Plot of average runtime for LP with an increasing number of divisions}
%	\label{fig:avg-runtime-divisions}
%\end{figure}

@@

We evaluate the effect of a longer time-horizon on the runtime of the algorithm. Figure \ref{fig:avg-runtime-blocks} presents the average runtime over 10 runs for an increasing number of 2-week blocks $B = \{26, 52, 78, 104\}$ to simulate a department that generates schedules for a few years in advance. We can see that there is an increasing trend in the runtime, however the solver is still able to find an optimal schedule for a 4-year time horizon in a very reasonable amount of time. \\

@@

Lastly, we analyze the effect of increasing the number of divisions on the runtime of the program. Table \ref{tbl:runtime-divisions-comparison} presents the runtime for $D = \{1, 2, 3\}$ divisions and $C = \{10, 20, 30, 50\}$ clinicians in total across all divisions. For 2 divisions, a roster of more than 20 clinicians becomes impractical, if all constraints must be satisfied, but the runtime can be improved if we allow consecutive blocks to be assigned. For 3 divisions, the problem becomes impractical faster, with any more than 10 clinicians leading to unreasonable runtime for finding an optimal solution, and the problem cannot be improved by relaxing the consecutive blocks constraint.

\include{tbl/runtime_divisions}
